\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-03-04 doc/USER_MANUAL/04_creating_databases.tex
corrects typos

\vspace{1cm}
\noindent {\bf $\bullet$ Absorbing boundary conditions setup}
\begin{description}
\item [{\texttt{PML\_CONDITIONS}}] Set to \texttt{.true.} to turn on C-PML
boundary conditions for a regional simulation. Both fluids and elastic solids are supported.
\item [{\texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.}
to turn on C-PML boundary conditions on the top surface instead of
the usual free surface.
\item [{\texttt{f0\_FOR\_PML}}] Determines the dominant frequency that
will be used in the calculation of PML damping profiles;
\red{This should be set to the same (or similar) dominant frequency as that of the
source that you will use in your simulation. It is \textbf{VERY IMPORTANT} to do that, otherwise the PML
absorbing conditions can become unstable.}
If you plan to use a Dirac source, then use the dominant frequency of the source wavelet
with which you plan to convolve your seismograms later on in post-processing.
\item [{\texttt{STACEY\_ABSORBING\_CONDITIONS}}] Set to \texttt{.true.}
to turn on Clayton-Enquist absorbing boundary conditions (see \citet{KoTr99}).
In almost all cases it is much better to use CPML absorbing layers
(see the options above) and leave this flag to \texttt{.false.}.
\item [{\texttt{STACEY\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.}
to turn on absorbing boundary conditions on the top surface which
by default constitutes a free surface of the model.
\item [{\texttt{BOTTOM\_FREE\_SURFACE}}]
When STACEY\_ABSORBING\_CONDITIONS is set to .true. :
absorbing conditions are defined in xmin, xmax, ymin, ymax and zmin
this option BOTTOM\_FREE\_SURFACE can be set to .true. to
make zmin free surface instead of absorbing condition.
\end{description}

>>>>

\vspace{1cm}
\noindent {\bf $\bullet$ Absorbing boundary conditions setup}
\begin{description}
\item [{\texttt{PML\_CONDITIONS}}] Set to \texttt{.true.} to turn on C-PML
boundary conditions for a regional simulation. Both fluids and elastic solids are supported.
\item [{\texttt{PML\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.}
to turn on C-PML boundary conditions on the top surface instead of
the usual free surface.
\item [{\texttt{f0\_FOR\_PML}}] Determines the dominant frequency that
will be used in the calculation of PML damping profiles;
\red{This should be set to the same (or similar) dominant frequency as that of the
source that you will use in your simulation. It is \textbf{VERY IMPORTANT} to do that, otherwise the PML
absorbing conditions can become unstable.}
If you plan to use a Dirac source, then use the dominant frequency of the source wavelet
with which you plan to convolve your seismograms later on in post-processing.
\item [{\texttt{STACEY\_ABSORBING\_CONDITIONS}}] Set to \texttt{.true.}
to turn on Clayton-Engquist absorbing boundary conditions (see \citet{KoTr99}).
In almost all cases it is much better to use CPML absorbing layers
(see the options above) and leave this flag to \texttt{.false.}.
\item [{\texttt{STACEY\_INSTEAD\_OF\_FREE\_SURFACE}}] Set to \texttt{.true.}
to turn on absorbing boundary conditions on the top surface which
by default constitutes a free surface of the model.
\item [{\texttt{BOTTOM\_FREE\_SURFACE}}]
When STACEY\_ABSORBING\_CONDITIONS is set to .true. :
absorbing conditions are defined in xmin, xmax, ymin, ymax and zmin
this option BOTTOM\_FREE\_SURFACE can be set to .true. to
make zmin free surface instead of absorbing condition.
\end{description}
